The \dealii{} Library, Version 9.3

### 2021-06-19 9.3/paper.tex
HZG -> Hereon
elaborate on changes, add email

\author[9,12]{Peter Munch}
 \affil[12]{Institute of Materials Research, Materials Mechanics,
 Helmholtz-Zentrum Geesthacht,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hzg.de}}}

@@

\author[14]{Konrad Simon}
  \affil[14]{Department of Mathematics/Center for Earth System Research and Sustainability (CEN),
  University of Hamburg, Grindelberg 5, 20144 Hamburg, Germany}

@@

  \item Previously, functions and classes were marked using the 
  macro \texttt{DEAL\_II\_DEPRECATED} and then typically removed in
  the release after the one in which these deprecation notices were
  available to users. We have now extended this policy by introducing
  the \texttt{DEAL\_II\_\allowbreak DEPRECATED\_EARLY} macro, which indicates that a feature will be
  deprecated in the next release. In contrast to the first macro, it will only give
  warnings if \dealii{} has been configured with \texttt{-D DEAL\_II\_EARLY\_DEPRECATIONS=ON}.
  \item After each update of the master branch of \dealii{}, we build a new Docker image
  with all features enabled. It is
  accessible on \texttt{Docker Hub} via \texttt{dealii/dealii:master-focal}. This image is
  particular useful when used in the continuous-integration processes of user codes.
\end{itemize}
%
The changelog lists more than 200 other features and bugfixes.

>>>>

\author[9,12]{Peter Munch}
 \affil[12]{Institute of Material Systems Modeling,
 Helmholtz-Zentrum Hereon,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hereon.de}}}

@@

\author[14]{Konrad Simon}
  \affil[14]{Department of Mathematics/Center
  for Earth System Research and Sustainability (CEN), University of
  Hamburg, Grindelberg 5, 20144 Hamburg, Germany.
  \texttt{konrad.simon@uni-hamburg.de}}}

@@

  \item Previously, functions and classes were marked using the 
  macro \texttt{DEAL\_II\_DEPRECATED} and then typically removed in
  the release after the one in which these deprecation notices were
  available to users. We have now extended this policy by introducing
  the \texttt{DEAL\_II\_\allowbreak DEPRECATED\_EARLY} macro, which indicates that a feature will be
  deprecated in the next release. In contrast to the first macro, it will only give
  warnings if \dealii{} has been configured with \texttt{-D DEAL\_II\_EARLY\_DEPRECATIONS=ON}.

  \item After each update of the master branch of \dealii{}, we build a new Docker image
  with all features enabled. It is
  accessible on \texttt{Docker Hub} via \texttt{dealii/dealii:master-focal}. This image is
  particular useful when used in the continuous-integration processes of user codes.

  \item A long standing orientation issue for the vector valued finite
  element \texttt{FE\_RaviartThomas<3>} was resolved. This issue
  prevented the user from using this class on meshes with cells that
  do not have standard orientation, i.e., cells that have faces that
  are flipped and rotated relative to their neighbors. In all eight
  possible neighboring configurations we can now guarantee that the
  necessary $H(\mathrm{div})$-conformity condition is met for all
  polynomaial orders. This is verified through a new conformity test
  on non-standard meshes.
\end{itemize}
%
The changelog lists more than 200 other features and bugfixes.
